*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-22 Code/Manuscript_O2.Rmd
introduction edits

We therefore analyzed the growth and physiological responses of representative strains from three clades ofr *P. marinus* under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods, to approximate eco-physiological conditions representative of current and hypothetical future ocean zones. *P. marinus* MED4, a clade HLI strain, was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal. *P. marinus* SS120, a clade LLIII strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P. marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m. At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].

@@

>>>>

We used the OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) to analyze the distribution of proteins from clades of *P. marinus* in samples tanken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling. We therefore analyzed the growth and physiological responses of representative strains from three clades ofr *P. marinus* under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods, to approximate eco-physiological conditions representative of current and hypothetical future ocean zones. *P. marinus* MED4, a clade HLI strain, was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal. *P. marinus* SS120, a clade LLIII strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P. marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m. At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].

@@

We discuss our findings in relation to analyses of genomic sequences CITATIONS across clades of *P. marinus*, showing that differences in the presence of genes encoding oxygen-dependent enzymes, and DNA repair enzymes, can help explain differential growth responses of strains under the matrix of light and [O~2~].
